Trends in asymmetric drift across the blue cloud

### 2018-04-30 ms.tex
merge vf fitting

Asymmetric drift (AD) is the lag of the mean rotation velocity of the
stellar disk behind the circular speed defined by the total
gravitational potential.  Although it is often considered a nuisance
correction one must apply in circular-speed calculations, the direct
connection between AD and the stellar phase-space distribution function
makes it an interesting dynamical properties of galaxies in and of
itself.  The SDSS-IV/MaNGA survey provides more than an order of
magnitude increase in any galaxy sample size useful for AD measurements.
In this pilot study, we measure AD --- or more precisely the
differential tangential lag between the stellar component and
\halpha-emitting gas --- in a set of galaxies with \halpha\ and stellar
velocity fields that are well-fit by simple disk models.  We describe
our fitting approach and the selection of our subsample in detail.  Our
final sample of $\sim$XXX galaxies shows a clear correlation between
absolute $i$-band magnitude and AD measured at effectively all radii.
\comment{The rest neesds to be updated.} Removing the primary dependence
on the rotation speed, we find that the stellar disk rotation is 90\% of
the \halpha\ rotation speed, in the mean.  Our sample size allows us to
infer a weak, yet statistically significant, trend with galaxy $N-r$
color such that, in the mean, redder galaxies have moderately larger AD
relative to their rotation speeds.  Within the context of an albeit
strong set of assumptions, including a direct proportionality between AD
and stellar velocity dispersion as seen in the Milky Way, we argue that
our results suggest little variation in the mean disk mass-to-light
ratio as a function of absolute magnitude and only modest variations
with galaxy color \comment{last sentence TBD; is Figure 3 consistent
with SPS variations?}.

@@

For ensembles of stars in a galaxy disk, \citet[][Section
4.4.3]{2008gady.book.....B} provide an intuitive description of
asymmetric drift (AD).  The combined effect of the radially decreasing
surface-density and velocity-dispersion profiles, typical of
axisymmetric systems like the Milky Way, leads to an asymmetric velocity
distribution function with a mean value less than the circular speed
defined by the gravitational potential.  The standard mathematical
representation of this is derived by taking the $v_R$ moment of the
collisionless Boltzmann equation to find the Jeans equation
\citep{Jeans1919} that directly relates the circular speed ($v_c$), the
mean stellar tangential speed ($\overline{v_\theta}$), and the stellar
velocity ellipsoid (SVE) as a function of radius in the plane of
symmetry:
%
\begin{equation}
%
v_c^2 - \overline{v_\theta}^2 = \sigma_R^2\left[
\frac{\sigma_\theta^2}{\sigma_R^2} -
\frac{R}{\rho\sigma_R^2}\frac{\partial(\rho\sigma_R^2)}{\partial R} -
1\right] - R\frac{\partial\overline{v_R v_z}}{\partial z},
%
\label{eq:adformal}
%
\end{equation}
%
where $R,\theta,z$ are the cylindrical coordinates, $\rho$ is the volume
density, and $\sigma$ is the velocity dispersion.  Along with the
standard assumptions of dynamical equilibrium and negligible radial and
vertical flows inherent to its derivation, equation \ref{eq:adformal} is
often simplified by assuming the right-most term --- describing the
covariance between the radial and vertical motions as a function of
perpendicular distance to the plane of symmetry --- is negligible
\citep[cf.][]{1991ApJ...368...79A}.

@@

Asymmetric drift measurements in extragalactic systems are common in the
literature \ref{examples}; however, it is most often cast as a nuisance
phenomenon that one must correct for when constructing circular-speed
curves \comment{refs}.  The ubiquity and phenomenology of AD as a
salient observable has not yet been studied for a statistically
significant population of galaxies.  Our aim is therefore to provide a
first look at the correlation between AD measurements and basic
broad-band photometric properties for a large sample of galaxies.

@@

In addition to a basic characterization of the phenomenon, our interest
in AD stems from its fundamental dynamical connection to the full
phase-space distribution function of a galaxy's stars, as empirically
demonstrated in the Milky Way.  Indeed, \citet{2011ApJ...742...18W} used
AD to constrain the axial ratios of the SVE given direct measurements of
the line-of-sight (LOS) stellar velocity dispersion, $\sigma$.
Alternatively, if one can leverage statistical constraints on the shape
of the SVE \citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can
be used as a proxy for stellar $\sigma$ via equation \ref{eq:adformal}.
Such a use of AD-$\sigma$ relation is attractive in the
low-surface-brightness and low-velocity-dispersion regimes where direct
measurements are difficult and/or expensive.  We commit to this paradigm
by defining $\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2$, following
from equation \ref{eq:adformal}, for use throughout this paper.

For disk galaxies, there is a decades-long industry of using cold-gas
tracers to construct circular-speed curves of galaxies \comment{refs}.
These data have provided the first concrete arguments for the presence
of massive dark-matter halos \comment{ref} based on mass-model
reconstruction \comment{refs} and have formed the basis for the most
robust Tully-Fisher relations compiled for the local Universe
\comment{refs}.  However, it is important to acknowledge that one cannot
directly measure $v_c$, effectively making $\sigma_a$ unobservable.
That is, every dynamical tracer has some non-zero dynamical pressure
such that it will lag behind the theoretically defined circular speed.
There are very clear examples of early-type galaxies that show
differential AD in their molecular (e.g., CO), atomic (e.g.,
\ion{H}{1}), and/or ionized (\halpha) tracers relative to a robust mass
model of $v_c$ \citep{2013MNRAS.429..534D}, due to the different
turbulent/thermal pressures intrinsic to these tracers.  However, these
signatures are much less apparent in disk galaxies.  For example,
\citet{2013A&A...557A.131M} show that \halpha\ and \ion{H}{1} rotation
curves are consistent for the DiskMass Survey within the limits of their
constraints on beam-smearing.  This suggests that any correction for the
lag behind the circular speed of either the \halpha- or
\ion{H}{1}-emitting gas should be small.  Indeed, theoretical
calculations \citet{2010ApJ...721..547D} suggest that gas-pressure
corrections to \ion{H}{1} rotation curves should be largely negligible
for galaxies with circular speeds larger than roughly 75 \kms.
Nevertheless, we emphasize here that our measurements of $\sigma_a$ may
be better termed as a {\em differential tangential lag} because they are
calculated as the quadrature difference between the {\em observed}
\halpha\ and stellar rotation curves in our galaxy sample (Section
\ref{sec:data}).  These measurements are perfectly valid in their own
right; however, their interpretation in the context of the theoretical
definition of AD must be done with care, as we discuss in Section
\ref{sec:discussion}.

We present the data used for our analysis in the following section.
Section \ref{sec:results} presents the strong correlation seen in out
galaxy sample between the absolute $i$-band magnitude and AD signal
measured at half of an effective radius (0.5 $R_{\rm eff}$).  We also
illustrate the weak color dependence in this relation.  Finally, we
summarize and discuss these results in Section \ref{sec:discussion}.
\comment{flesh out}

@@

@@

The kinematic measurements are determined by a preliminary version of
the MaNGA data analysis pipeline (DAP; Westfall et al., in prep).  From
this preliminary version (2.0.2), we use the simple single-Gaussian fits
to the \halpha\ emission feature for the ionized-gas kinematics, and the
stellar kinematics are determined using {\tt pPXF}
\citep{2004PASP..116..138C, 2017MNRAS.466..798C} with the MILES stellar
template library \citep{2011A&A...532A..95F}.  We find the velocity
measurements to be statistically well behaved to a $g$-band
signal-to-noise ratio (SNR) of $\sim$1.\footnote{
%
This and other assessments of the fidelity of the stellar kinematics
provided by the DAP will be discussed in detail by Westfall et al., {\em
in prep}.}
%
Therefore, we perform our analysis using the stellar kinematics measured
for each MaNGA spaxel (each spaxel is $0\farcs5$ on a side and
subsamples the $\sim$$2\farcs5$ fiber beam).

% \comment{Mention hierarchical clustering?}

The MaNGA galaxy selection, see \citet{2017AJ....154...86W}, is a simple
cut in absolute $i$-band magnitude, $M_i$, from the NASA-Sloan Atlas
(NSA; \url{www.nsatlas.org}) and the SDSS single-fiber redshift, $z$.
The MaNGA galaxy sample provides a statistically complete representation
of the overall galaxy population with a provided set of corrections to a
volume-limited sample.  The NSA-based ($N-r, M_i$) color-magnitude
diagram (CMD) of the full sample of galaxies obtained through the second
year of survey operations are shown in the left-most panels of Figure
\ref{fig:sample}, with the points colored by the \halpha\ .

\comment{Update this} Although not
excluded from our velocity-field analysis {\em a priori}, we expect to
obtain poor rotation-curve measurements for galaxies with low \halpha\
and stellar surface brightness.\footnote{
%
The uniformity of the MaNGA survey \citet{2015AJ....150...19L} is such
that the signal-to-noise (S/N) of the datacube spaxels is tightly
correlated with surface brightness.}

>>>>

Asymmetric drift (AD) is the lag of the mean rotation velocity of the
stellar disk behind the circular speed defined by the total
gravitational potential.  Although it is often considered a nuisance
correction one must apply in circular-speed calculations, the direct
connection between AD and the stellar phase-space distribution function
makes it an interesting dynamical property of galaxies in and of itself.
The SDSS-IV/MaNGA survey provides more than an order of magnitude
increase in any galaxy sample size useful for AD measurements.  In this
pilot study, we measure AD --- or more precisely the differential
tangential lag between the stellar component and \halpha-emitting gas
--- in a set of galaxies with \halpha\ and stellar velocity fields that
are well-fit by simple disk models.  We describe our fitting approach
and the selection of our subsample in detail.  Our final sample of
$\sim$XXX galaxies shows a clear correlation between absolute $i$-band
magnitude and AD measured at effectively all radii.  \comment{The rest
neesds to be updated.} Removing the primary dependence on the rotation
speed, we find that the stellar disk rotation is 90\% of the \halpha\
rotation speed, in the mean.  Our sample size allows us to infer a weak,
yet statistically significant, trend with galaxy $N-r$ color such that,
in the mean, redder galaxies have moderately larger AD relative to their
rotation speeds.  Within the context of an albeit strong set of
assumptions, including a direct proportionality between AD and stellar
velocity dispersion as seen in the Milky Way, we argue that our results
suggest little variation in the mean disk mass-to-light ratio as a
function of absolute magnitude and only modest variations with galaxy
color \comment{last sentence TBD; is Figure 3 consistent with SPS
variations?}.

@@

For ensembles of stars in a galaxy disk, \citet[][Section
4.4.3]{2008gady.book.....B} provide an intuitive description of
asymmetric drift (AD).  The combined effect of the radially decreasing
surface-density and velocity-dispersion profiles, typical of
axisymmetric systems like the Milky Way, leads to an asymmetric velocity
distribution function with a mean value less than the circular speed
defined by the gravitational potential.  The standard mathematical
representation of this is derived by taking the $v_R$ moment of the
collisionless Boltzmann equation to find the Jeans equation
\citep{Jeans1919} that directly relates the circular speed ($v_c$), the
mean stellar tangential speed ($\overline{v_\theta}$), and the stellar
velocity ellipsoid (SVE) as a function of radius in the plane of
symmetry:
%
\begin{equation}
%
v_c^2 - \overline{v_\theta}^2 = \sigma_R^2\left[
\frac{\sigma_\theta^2}{\sigma_R^2} -
\frac{R}{\rho\sigma_R^2}\frac{\partial(\rho\sigma_R^2)}{\partial R} -
1\right] - R\frac{\partial\overline{v_R v_z}}{\partial z},
%
\label{eq:adformal}
%
\end{equation}
%
where $R,\theta,z$ are the cylindrical coordinates, $\rho$ is the volume
density, and $\sigma$ is the velocity dispersion.  Along with the
standard assumptions of dynamical equilibrium and negligible radial and
vertical flows inherent to its derivation, equation \ref{eq:adformal} is
often simplified by assuming the right-most term is negligible
\citep[cf.][]{1991ApJ...368...79A}; i.e., there is negligible covariance
between the radial and vertical motions as a function of perpendicular
distance to the plane of symmetry.

@@

Asymmetric drift measurements in extragalactic systems are common in the
literature \comment{examples}; however, it is most often cast as a nuisance
phenomenon that one must correct for when constructing circular-speed
curves \comment{refs}.  The ubiquity and phenomenology of AD as a
salient observable has not yet been studied for a statistically
significant population of galaxies.  Our aim is therefore to provide a
first look at the correlation between AD measurements and basic
broad-band photometric properties for a large sample of galaxies.

@@

In addition to a basic characterization of the phenomenon, our interest
in AD stems from its fundamental dynamical connection to the full
phase-space distribution function of a galaxy's stars, as empirically
demonstrated in the Milky Way.  Indeed, \citet{2011ApJ...742...18W} used
AD to constrain the axial ratios of the SVE given direct measurements of
the line-of-sight (LOS) stellar velocity dispersion, $\sigma$.
Alternatively, if one can statistically constrain the shape of the SVE
\citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD could then be
used as a proxy for stellar $\sigma$ via equation \ref{eq:adformal}.
Such an AD-$\sigma$ relation becomes attractive in the
low-surface-brightness and low-velocity-dispersion regimes where direct
measurements of $\sigma$ are difficult and/or expensive.  Adopting this
paradigm outright, we define $\sigma_a^2 \equiv v_c^2 -
\overline{v_\theta}^2$, following from equation \ref{eq:adformal}, for
use throughout this paper.

For disk galaxies, there is a decades-long industry of using cold-gas
tracers to construct circular-speed curves of galaxies \comment{refs}.
These data have provided the first concrete arguments for the presence
of massive dark-matter halos \comment{ref} based on mass-model
reconstruction \comment{refs} and have formed the basis for the most
robust Tully-Fisher relations compiled for the local Universe
\comment{refs}.  However, it is important to acknowledge that one cannot
directly measure $v_c$, effectively making $\sigma_a$ unobservable.
That is, every tracer has some non-zero dynamical pressure such that it
will lag behind the theoretically defined circular speed.  There are
very clear examples of early-type galaxies that show differential AD in
their molecular (e.g., CO), atomic (e.g., \ion{H}{1}), and/or ionized
(\halpha) tracers relative to a robust mass model of $v_c$
\citep{2013MNRAS.429..534D} due to the different turbulent/thermal
pressures intrinsic to these tracers.  However, these signatures are
much less apparent in disk galaxies.  For example,
\citet{2013A&A...557A.131M} show that \halpha\ and \ion{H}{1} rotation
curves are consistent for the DiskMass Survey within the limits of their
constraints on beam-smearing.  This suggests that any correction for the
lag behind the circular speed of either the \halpha- or
\ion{H}{1}-emitting gas should be small.  Indeed, theoretical
calculations \citet{2010ApJ...721..547D} suggest that gas-pressure
corrections to \ion{H}{1} rotation curves should be largely negligible
for galaxies with circular speeds larger than roughly 75 \kms.
Nevertheless, we emphasize here that our measurements of $\sigma_a$ may
be better termed as a {\em differential tangential lag} because they are
calculated as the quadrature difference between the {\em observed}
\halpha\ and stellar rotation curves in our galaxy sample (Section
\ref{sec:data}).  These measurements are perfectly valid in their own
right; however, their interpretation in the context of the theoretical
definition of AD must be done with care, as we discuss in Section
\ref{sec:discussion}.

\comment{Outline should be updated} We present the data used for our
analysis in the following section.  Section \ref{sec:results} presents
the strong correlation seen in out galaxy sample between the absolute
$i$-band magnitude and AD signal measured at half of an effective radius
(0.5 $R_{\rm eff}$).  We also illustrate the weak color dependence in
this relation.  Finally, we summarize and discuss these results in
Section \ref{sec:discussion}.  \comment{flesh out}

@@

\subsection{Galaxy Sample}

@@

The MaNGA galaxy selection is discussed in detail by
\citet{2017AJ....154...86W}; the galaxies in DR14 represent a random
sampling of full MaNGA parent sample.  The parent sample is selected
using simple cuts in absolute $i$-band magnitude, $M_i$, and redshift,
$z$, from the NASA-Sloan Atlas (NSA; \url{www.nsatlas.org}) to produce
two main galaxy samples, Primary and Secondary, with roughly twice as
many galaxies observed from the former.  The main distinguishing
characteristic of the two samples is MaNGA provides uniform coverage to
$\sim$$1.5R_e$ and $\sim$$2.5R_e$ for the Primary and Secondary sample,
respectively.  The Primary sample is supplemented by a
``Color-enhanced'' sample that improves coverage of the galaxy
population in low-density regions of color-magnitude space; the
combination of Primary and Color-enhanced samples are referred to as the
Primary$+$ sample.  Although we will comment on any difference in our
analysis results between the Primary$+$ and Secondary samples, we
largely treat these two samples identically in our analysis.

The ($N-r, M_i$) color-magnitude diagram (CMD) for MaNGA galaxies in
DR14 (using NSA photometry) is shown in the left-most panels of Figure
\ref{fig:sample}.  Data in the top and bottom row are colored according
to, respectively, the average \halpha\ surface brightness and
$g$-band-weighted mean flux density within 1 $R_e$.  We discuss Figure
\ref{fig:sample} in the context of our selection of galaxies appropriate
for our AD analysis \comment{below}.

\subsection{MaNGA Spectroscopy}

The MaNGA fiber-feed system \citet{2015AJ....149...77D} for the
2.5-meter Sloan telescope at Apache Point Observatory (APO) is coupled
to the SDSS-III/BOSS spectrographs \citep{2013AJ....146...32S}, a pair
of dual-channel spectrographs that provide $R_\lambda =
\lambda/\Delta\lambda \approx 2000$ across the full spectral range of
$3600\AA \lesssim \lambda \lesssim 10300\AA$.  Each MaNGA pointing
provides simultaneous observations of 17 galaxies using fiber bundles
ranging from 19 to 127 fibers.  The dither pattern of the MaNGA
observational strategy \citep{2015AJ....150...19L} provides a remarkably
uniform depth for each observation with fields-of-view ranging from
$12\arcsec$ to $32\arcsec$ for the smallest and largest bundles,
respectively.  The uniform depth yields a tight correlation between flux
density per spaxel and signal-to-noise (S/N); see
\citet{2015AJ....150...19L, 2016AJ....152...83L} and
\citet{2016AJ....151....8Y, 2016AJ....152..197Y} for additional details
about the survey execution and performance.

In particular, \citet{2016AJ....152...83L} describes the methods used by
the MaNGA Data Reduction Pipeline (DRP) is an to produce wavelength-,
flux- \citep{2016AJ....151....8Y}, and astrometrically calibrated
spectra from the raw CCD data.  The reduction procedures are similar to
those used by the SDSS-III/BOSS pipeline, but with significant
adjustments as required by the MaNGA observations.

Here, we use the rectified datacubes that have been logarithmically
binned in wavelength (i.e., the \verb|LOGCUBE| files).  The MaNGA data
cubes are constructed by regridding the flux of all spectra for a given
plate--IFU combination in each wavelength channel to an on-sky pixel
(spaxel) sampling of $0\farcs5\times0\farcs5$.  The interpolating PSF
used in this process is a two-dimensional Gaussian with a standard
deviation of $0\farcs6$ and a truncation radius of $1\farcs7$.  This
interpolation process leads to significant covariance between the
spaxels in a given wavelength channel \citep{2016AJ....152...83L}.  This
spatial covariance does not affect the primary result of our paper, so
we defer a more detailed consideration of the covariance for future
work.

\subsection{Stellar and Ionized-Gas Kinematics}

The kinematic measurements are determined by a preliminary version
(2.0.2) of the MaNGA Data Analysis Pipeline (DAP; Westfall et al., {\it
in prep}).  The pipeline provides simple single-Gaussian fits to the
\halpha\ emission feature that we use for the ionized-gas kinematics,
and the stellar kinematics are determined using {\tt pPXF}
\citep{2004PASP..116..138C, 2017MNRAS.466..798C}.  The templates used by
{\tt pPXF} are a hierarchically clustered distillation of the MILES
stellar template library \citep{2011A&A...532A..95F}.  We find the
velocity measurements to be statistically well behaved to a $g$-band
signal-to-noise ratio of S/N$\sim$1.\footnote{
%
This and other assessments of the fidelity of the stellar kinematics
provided by the DAP will be discussed in detail by Westfall et al., {\it
in prep}.}
%
Therefore, we perform our analysis using the spaxel-by-spaxel
determination of the stellar and ionized-gas kinematics.\footnote{
%
However, note that only the stellar kinematic determined for data
Voronoi binned to S/N$\sim$10 will be provided as part of DR15.}

\section{Velocity-Field Modeling}

\subsection{Formalism}

We fit the \halpha and stellar velocity fields using an approach similar
to \citet{2013ApJ...768...41A} \citep[][see also
\citealt{2011ApJ...742...18W}].  The velocity field is modeled as an
infinitely thin disk in fully circular rotation that follows a
parameterized form $V_{\rm rot}(R)$; here we use a simple hyperbolic
tangent function:
%
\begin{equation}
%
V_{\rm rot}(R) = V_\infty \tanh(R/h_{\rm rot}),
%
\label{eq:tanh}
%
\end{equation}
%
where $V_\infty$ is the asymptotically flat rotation speed and $h_{\rm
rot}$ is a characteristic scale for the rise of the rotation curve, and
the model line-of-sight (LOS) velocity is
%
\begin{equation}
%
V_{\rm los}(x,y) = V_{\rm rot}(R[x,y])\ \cos(\theta[x,y])\ \sin i +
V_{\rm sys}
%
\label{eq:vlos}
%
\end{equation}
%
where $i$ is the disk inclination (a ``face-on'' disk has $i=0$), and
$V_{\rm sys}$ is the systemic velocity of the galaxy.  The disk-plane
polar coordinates ($R,\theta$) in Equation \ref{eq:vlos} are functions
of the on-sky position:
%
\begin{eqnarray}
%
x_d & = & (x+x_0)\sin\phi_0 + (y+y_0)\cos\phi_0 \\
%
y_d\cos i  & = & -(x+x_0)\cos\phi_0 + (y+y_0)\sin\phi_0 \\
%
R^2 & = & x_d^2 + y_d^2 \\
%
\tan\theta & = & -y_d / x_d,
%
\label{eq:diskrt}
%
\end{eqnarray}
%
where ($x,y$) is the on-sky position ($+$$x$ is to the east) relative to
the center of the object as defined by the targeting catalog,
($x_0,y_0$) is the location of this pointing center of the IFU relative
to the dynamical center, $\phi_0$ is the position angle defined from
north through east of the receding side of the major axis, and
($x_d,y_d$) are the disk-plane Cartesian coordinates.  Note that
$\theta=0\arcdeg$ along the major axis on the receding side of the
galaxy.

\comment{REST IS OLD TEXT}

[[We emphasize that this parametrization is used in the determination of
the kinematic geometry from the rotation curve, but not as measurements
of the rotation speed itself (see Section XX).]]

Provided $j=0...N_{\rm spaxels}$ LOS velocity measurements, $V_{{\rm
los},j}$, and their errors, $\epsilon_{v,j}$, we determine the
best-fitting model velocity field using a Levenberg-Marquardt
minimization algorithm with the following figure-of-merit:
%
\begin{equation}
%
\chi^2 = \sum_j \frac{ (V_{{\rm los},j}-V_{\rm mod}[x_j,y_j])^2 }{
\epsilon^2_{v,j} + \epsilon^2_{\rm mod}},
%
\label{eq:vfchi}
%
\end{equation}
%
where $\epsilon_{\rm mod}$ is an intrinsic scatter of the measured LOS
velocities about the simplistic model.  To simplify further discussion,
we denote the $j$ components of the sum on the right-hand of the
equation as $\chi^2_j$. [[Go back and include the ``beam-smearing''
term?]]

In an effort to minimize the well-known covariance between the
inclination and rotation speed (refs), our velocity-field
parameterization actually fits the {\em projected} rotation curve (i.e.,
$V_{\rm rot}(R) \sin i$) instead of the disk-plane rotation speed
itself.  The fitted parameters for a single velocity field are then
$x_c$, $y_c$, $i$, $\phi_0$, $V_{\rm sys}$, $V_\infty \sin i$, and
$h_{\rm rot}$.

\subsubsection{Implementation details}
\label{sec:vfimplement}

The description in Section \ref{sec:vfbasic} [[apart from leaving out
the beam-smearing term]] is identical to the approach of
\citet{2013ApJ...768...41A}.  The alterations specific to our
implementation are as follows \citep[cf.][]{2011ApJ...742...18W}:

\begin{enumerate}
%
\item {\em Simultaneous VF fitting}:  We have extended the code from
\citet{2013ApJ...768...41A} to allow for simultaneous fits to multiple
dynamical tracers, while allowing the rotation curves of the two
components to be different.  Although we do fit the \halpha and stellar
data fit independently, this is primarily used in the selection cuts
imposed in Section \ref{sec:kingeomcuts}.  When fitted simultaneously,
there are three additional free parameters compared to those listed
above: the two additional rotation curve parameters and systemic
velocity of the second dynamical tracer.  That is, even when fitting the
two velocity fields simultaneously, we allow for the systemic velocities
of the two tracers to be different.  This is primarily to allow for,
e.g., systematic errors in the velocity registration of the template
libraries used to determine the stellar kinematics.  Ideally, one would
like to force the systemic velocities of the two tracers to be the same,
and we discuss the effects on our results by allowing them to be
different in Section \ref{sec:kingeom}.
%
\item{\em Intrinsic scatter}:  The intrinsic scatter term,
$\epsilon_{\rm mod}$, serves a number of purposes.  Its effect is to
alter the error-weighted distribution of the fit residuals such that it
closely follows a Gaussian distribution with unity standard deviation;
that is, it forces the reduced $\chi^2$, $\chi^2_\nu$, of the fit to be
very close to unity.  Indeed, \citet{2013ApJ...768...41A} chose
$\epsilon_{\rm mod}$ such that $\chi^2_\nu$$\sim$1 to within 1\%.  Our
approach is to instead iteratively adjust $\epsilon_{\rm mod}$ until the
growth curve of $\chi^2_j$ is marginally different from the growth curve
of a Gaussian function with unity standard deviation.  This approach is
primarily chosen given its advantage in dealing with our third
alteration. [[Affect on formal parameter errors from the covariance
matrix.]]
%
\item{\em Measurement Rejection}:  The fits to the velocity fields
generally provide $\chi^2_\nu > 1$ when $\epsilon_{\rm mod} = 0$,
meaning that there is a general systematic discrepancy of model with
respect to the $V_{\rm los}$ measurements that is not accounted for by
the random errors, $\epsilon_{v,j}$.  Although most of the discrepancies
can be accounted for by a small ($\epsilon_{\rm mod}\sim XX$) scatter
about the simplistic model, systematic error in the kinematic
measurements, particularly at low SNR, can lead to a number of
$V_{{\rm los},j}$ with $\chi^2_j \gg 1$.  We iteratively reject these
data from the fit at the same time as we determine the intrinsic scatter
term, $\epsilon_{\rm mod}$.  After fitting the data with a given
$\epsilon_{\rm mod}$ (starting with 0), we iteratively reject points
with $\chi^2_j > 1$, starting with the largest value, and adjust
$\epsilon_{\rm mod}$ until the root-mean-square difference between the
growth curve of $\chi^2_j$ and a Gaussian with unity standard deviation
is minimized.  This whole process of fitting the velocity field,
determining $\epsilon_{\rm mod}$, and rejecting aberrant data is done
many times to make sure that the points that are rejected and the value
of $\epsilon_{\rm mod}$ is not strongly biased by the initial fit to the
velocity field.
%
\end{enumerate}

% [[I realize that the above two (maybe even all three) things are
% highly detailed.  We probably want to make them simpler.]]

\subsubsection{Initialization}
\label{sec:vfinit}

The MaNGA data cubes (cf. Law et al.~{\em in prep}) provide an accurate
registration of the spectrophotometry with on-sky imaging data to
provide a detailed astrometric calibration in the form of a
world-coordinate system (WCS) in the fits headers. The coordinates of
the targeted galaxy\footnote{
%
This is generally the center of the data cube field-of-view; however,
some observations were purposely offset for testing purposes.
%
} are, in general, exactly the coordinates provided by the NASA-Sloan
Atlas; however, some coordinates have been adjusted to better match the
galaxy center [[check this with David W.]] (cf., Wake et al.~{\em in
prep}).  The ($x,y$) coordinate system in Eqn. \ref{eq:vlos} is then
established by setting the (0,0) coordinate at the galaxy center.  Thus,
when freely fit, we should expect to find $x_0 = y_0 = 0$ arcsec.

The NASA-Sloan Atlas also provides ellipticity and position angle
measurements for isophotal contours of each galaxy, which we use as the
initial guesses for the kinematic inclination and position angle,
respectively.  For an oblate spheroid with intrinsic axial ratio $q_0$
and an observed ellipticity of $\varepsilon = 1-b/a$, its inclination to
the LOS is given by (ref)
%
\begin{equation}
%
\cos^2 i_{\rm phot} = \frac{ (1-\varepsilon)^2 - q_0^2 }{ 1 - q_0^2 }.
%
\label{eq:inc}
%
\end{equation}
%
For our measurements of $i_{\rm phot}$, we assume $q_0 = 1/8$ (Bershady;
but, cf., Weijmanns).

Given that our definition of $\phi_0$ is tied to the vector along the
major axis toward the receding side of the velocity field, the kinematic
position angle has a valid range of $2\pi$.  However, photometric
position angles only have a valid range of $\pi$.  Our initial guess of
$\phi_0$ is either the same as the photometric value or flipped by
$180\degr$ based on an initial deprojection of the rotation speed along
the photometric position angle.

Finally, we use the redshift provided by the NASA-Sloan Atlas as the
initial estimate of the systemic velocity, $V_{\rm sys} = c z_{\rm
NSA}$.

\subsubsection{Fitting iterations}
\label{sec:vfiter}

We expect AD to be present in all galaxies, and so we
attempt to fit all 1392 galaxies in the current MaNGA sample.  For such
a large galaxy sample, it is difficult to attempt human interaction at a
detailed level with each fit.  Therefore, all of the fits have been
performed in an automated way.  To help in the quality assessments of
the fits (Sections \ref{sec:kingeom} and \ref{sec:kingeomcuts}), we fit
the velocity fields of each tracer (\halpha-emitting gas and stars) both
individually and in a single, simultaneous fit.  Additionally, we
perform the individual and simultaneous fits under permutations of
fixing and freeing the inclination and center.

The determination of $V_{\rm sys}$ and $\phi_0$ are generally robust and
well-constrained by the data, meaning there is no need to fix them to
certain values.  Conversely, the inclination and center can be poorly
determined in certain regimes.  For example, when the observed velocity
field is that of a solid-body rotator, the isovelocity contours all
become parallel to the minor axis ($V_{\rm rot} \propto R$ and, at a
fixed perpendicular distance from the minor axis, $\cos\theta \propto
R^{-1}$).  Thus, in the absence of any other information, one could
place the center anywhere in the velocity field without affecting
$\chi^2$.  Similarly, measurements of inclination depend on the
curvature seen in the isovelocity contours and there is no such
curvature for a solid-body rotator.  Finally, at low inclination, the
curvature in the isovelocity contours can be imperceptible due to the
stochastic deviations (random and systematic) about the fitted model.
Therefore, by performing fits that both fix and free the center and
inclination, we can test the consistency of the results and the
significance of kinematically constrained parameters versus simply
adopting the photometric one.

In addition, we impose boundaries on the allowed range for the geometric
parameters.  We force the systemic velocity to be within $\pm1000$
\kms{} of the input guess, we force $0.1\leq i \leq 85$ and
$0\leq\phi_0<360$, and we define a bounding box for the fitted center to
be $\sim$20\% of the full field-of-view.  The limits for the IFUs with
19, 37, 61, 91, and 127 fibers are limited to $\pm1\arcsec$,
$\pm2\arcsec$, $\pm2\arcsec$, $\pm3\arcsec$, and $\pm3\arcsec$,
respectively.

In summary, we perform 12 velocity-field fits for each galaxy: (1) four
fits are permutations of fixing and freeing the center and inclination
and (2) each of these four fits is done when only fitting the \halpha
data, only fitting the stellar data, and fitting both tracers
simultaneously.
%
\begin{figure*}
%
\includegraphics[width=0.9\textwidth]{figs/sys_cen_pa.pdf}
%
\caption{
%
Distribution of (a) the difference between the \halpha and stellar
systemic velocities; (b) the center relative to the imposed fit
boundary; and (c) the difference between the \halpha and stellar kinematic
position angles.  For the center panel, the distributions of
$\tilde{x}_0$ and $\tilde{y}_0$ are shown as (transparent) light and
dark histograms, respectively.  The 3-sigma clipped mean ($\mu$) and
standard deviation ($\epsilon$) for each distribution is provided in
associated panel.  The dashed lines illustrate the cuts that we adopt
for each parameter in our AD analysis(see text).
%
}
%
\label{fig:sys_cen_pa_hist}
%
\end{figure*}

\subsection{Kinematic Geometry Results}
\label{sec:kingeom}

For our AD measurements, we require robustly measured kinematic
geometries that can be applied to both the \halpha-emitting and stellar
components.  This requirement drives our assessments of the kinematic
geometries and the selection of galaxies to propagate through our AD
analysis in the remaining sections of the paper.  For example, it is
physically plausible to find a significant offsets between the position
angles of gas and stars (e.g., Chen et al.; Belfiore et al.); however,
this is typically the signature of an accretion event and not conducive
to an AD measurement.  Given the fits that we have performed, we can
check both the consistency of the \halpha and stellar geometries, as well
as their consistency with the morphological geometry.

We first limit our assessments to those galaxies with successfully
converged velocity-field fits for all 12 fit iterations, which cuts our
sample from 1392 to 1322 galaxies.  [[Should maybe have a sentence about
why these failed?]]  All subsequent cuts include this base-level
selection.

\subsubsection{Systemic velocity}

When fit separately, the best-fitting systemic velocities for both the
\halpha and stellar data are in good agreement with each other and with
the redshifts in the NASA-Sloan Atlas, $cz_{\rm NSA}$.  The mean
difference with respect to $cz_{\rm NSA}$ over the full 1322 galaxies is
less than 10 \kms{} and the standard deviation is approximately the
velocity width of a spectral channel ($\sim$70 \kms{}), regardless of
the fitting constraints or tracer.

The result is approximately the same when considering the difference
between the \halpha-only and stellar-only fit parameters.  Indeed, we
should expect that the systemic velocity should be the same for the
\halpha and stellar components; however, we have allowed them to be
different, even when fitting the two velocity fields simultaneously.
Fig.~\ref{fig:sys_cen_pa_hist}(a) shows the distribution of $V_{{\rm
sys,H}\alpha} - V_{{\rm sys},\ast}$ when both are fit simultaneously.
After applying a 3-sigma clipping algorithm, we find a mean difference
of $2.3\pm6.8$ \kms{}.  It is difficult to understand how this
systematic offset could arise either physically or due to a
wavelength-calibration error.  We therefore assume that this mean offset
is due to a systematic error in the velocity registration of the MIUSCAT
template spectra across our fitted wavelength range.  Further work is
required to exactly address this problem; however, it has a minimal
effect on our analysis [[need to test this]].

To avoid the strong outliers, particular toward the negative end of
Fig.~\ref{fig:sys_cen_pa_hist}(a), we select only those galaxies with
-12.5 \kms{} $\leq V_{{\rm sys,H}\alpha} - V_{{\rm sys},\ast} \leq 17.5$
\kms{} for further analysis; 850 of 1322 galaxies (64\%) meet this
criterion.

\subsubsection{Pointing relative to the dynamical center}

In Section \ref{sec:vfiter}, we noted that the pointing relative to the
dynamical center ($x_0,y_0$) has a bounding box placed on it that is
IFU-dependent.  When selecting results for our AD analysis, we care more
about the fitted center relative to the bounding box than we do about
the absolute center in arcseconds.  Therefore, in
Fig.~\ref{fig:sys_cen_pa_hist}(b) we show the ratio of the fitted center
relative to the size of the bounding box --- e.g., $-1\leq \tilde{x}_0
\leq 1$ --- for both on-sky coordinates.  Recall (Section
\ref{sec:vfbasic}) the definition of our ($x,y$) coordinate system is
such that a result of $(x_0,y_0) = (0,0)$ means that the morphological
and dynamical centers are co-located.
